### 2021-02-13 results.tex
first pass in the results section

In this section, we present the finding of our study. We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study (Section V-C).

\subsection{Result of the first study: A non-exact replication}

Our first study performed a non-exact replication of Bao et al work. Our study differs from the original because in your study we isolated the effect of static analysis at our results of malicious apps detected by each mined sandbox. We could use all $102$ pairs apps (B/M) from the original study, because the benchmark tool could instrument six pair apps from Bao et al work, i.e., P25, P32, P36, P41, P88, and P93. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute. The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al. results.

We present the results of 96 pairs apps analyses, performing DroidXP benchmark with its default configuration, and then we performing DroidXP disabling the Droidfax static analysis algorithm, to investigate the number of malware detected by the sandbox, generated by the effective performance of the dynamic analysis tools, ignoring static analysis influence. Next, we report the detection capability of each tool in terms of malware detected.

\textbf{Droidbot} with DroidXP default configuration detects a total of 68 malware among $96$ pairs analyzed (70.83\%), the same number of apps find at original study, although the original study analyzed $102$ pairs, the percent is close. At the original study, Droidbot was the test case generation tool that detected the largest number of malicious apps, 68 among $102$ (66,66\%). However, when we disabling the static analysis, Droidbot has an efficiency reduction of 20.58 \%, and was able to detect $54$ malware. Despite this reduction, it had the largest number of malicious apps detected in this new situation.

\textbf{Monkey} at the first step, created a sandbox that could detect more apps with malicious behavior than the other tools analyzed, 71 among 96 pairs. Although the original study, it got the third-best performance, detecting 48 among 102 pairs investigated (47.05\%), the result between studies could vary due to its random exploration strategy. When disabling static analysis, its accuracy reduced to 23.94\%, totaling 54 malware detected, matching the detect capacity of Droidbot at this configuration.

\textbf{Droimate} with default configuration was able to detect 64 apps with malicious behaviors (66,66\%), and at the original study, it detected 54 among 102 (52.94\%). This minor variation may be caused due the original work used the oldest version of Droidmate, and our study used Droidmate 2 \cite{DBLP:conf/kbse/BorgesHZ18}, an improved version of the original DroidMate project, that we believe has a better mine strategy than his previous version and may have generated a more efficient sandbox. Disabling static analysis, Droidmate has its accuracy reduced at 25\%, being able to detect 48 among 96 pairs analyzed.

\textbf{Humanoid} at the first step of our study had the worse performance, identifying a little more than half of the pairs analyzed, 49 (51.04\%). It is the only tool not present at Bao et al work, so we could not compare our results with its work. Regarding the second part of the study, without static analysis, Humanoid was the most affected by this new situation, losing 69.38\% of its effectiveness, being able to detect just 15 pair apps malicious.

\textbf{Joke}, as described, is a fake tool, that simulates a test tool that does not execute Android apps during a benchmark execution, considering just static analysis results. Even though Joke tool does not execute the Android apps, it was responsible to detect 43.75\% of malware, only aided by static analysis Droidfax, at the default configuration. Ignoring the influence of static analysis, since Joke tool depends exclusively on static analysis Droidfax, we suppose that it sandbox was unable to detect malware at our data set, result confirmed in our study, where Joke was unable to detect any malware, reducing its sandbox accuracy in 100\%.

Except for the Joke dummy tool, our studies show that 73.95\%-51.04\% of malicious pairs apps investigated, can be detected by the sandboxes constructed by others selected test generation tools, with de DroidXP default configuration. This first setup of our first study also shows that all the constructed sandboxes did not identify the malware in 19 pairs among 96 (19.79\%). These 19 malicious apps, according to Euphony tool \cite{hurier2017euphony}, that infer a single label per malicious application based on VirusTotal, were: 13 adwares, 3 trojans, 2 PUP (Potentially Unwanted Program) and 1 exploit. Table \ref{tab:malware} presents the number of malware detected by the sandboxes designed for each test case generation tool, with DroidXP default configuration, with static analysis Droidfax aid.

@@

\subsection{Result of the second study: Tainted analysis algorithms.}

@@

\subsection{Result Summary}

>>>>

In this section we detail the findings of our study. We first present the results of each study
in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}. In Section~\ref{sec:discussion} we summarize the
implications of our study.

\subsection{Result of the first study: A non-exact replication}\label{sec:res-fs}

Our first study performed a non-exact replication of Bao et al work.
Our study differs from the original because here we isolated the effect
of the DroidFax static analysis algorithms in the performance to
identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the \original work.
\rb{All of this following information should be detailed in
the study settings, and not repeated here if it is already there.} {\color{red}We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute. The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al. results.}

As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of th execution. The columns Exec. (I) and Exec. (II) 
show the number of malwares identified when executing each tool (I) with the
support of the DroidFax static analysis algorithms and (II) withouth the support
of DroidFax static analysis algorithms. The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that this difference is in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for wich DroidFax improves its performance in 100\% (as expected).
Next we discuss the result of each individual test generation tool.

\begin{table}[ht]
  \caption{Summary of the results of the first study. }
  \centering
  \begin{small}
 \begin{tabular}{lrrr}
   \toprule
   Tool & Exec. (I) & Exec. (II) & Improvement (\%) \\   \midrule
  Monkey &  71 &  54 & 23.94 \\ 
  Droidmate &  64 &  48 & 25.00 \\ 
  Droidbot &  68 &  54 & 20.59 \\ 
  Humanoid &  49 &  15 & 69.39 \\ 
  \joke &  42 &   0 & 100.00 \\ 
 \bottomrule
 \end{tabular}
 \end{small}
 \label{tab:fs}
\end{table}

\subsubsection*{Monkey} sandbox for the first execution (Exec. (I)) detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps). Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%). This difference might be due to the Monkey randomic strategy for test case generation. \rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec. (II)), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of Droidbot for Exec. (II). \rb{Considering only one run for each configuration, that is Exec. (I) and Exec. (II), we cannot assure that the difference is due to disabling the DroidFax static analysis algorithms.}

\subsubsection*{Droidbot} in the first execution (Exec. (I)) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%). Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps. Also, in the original study, Droidbot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps. However, in our second execution (Exec. (II)), its performance decreased in 20.58 \%. \rb{Not sure if the following sentence is right.} Despite this reduction, it achieved the largest number of malicious apps detected in the second execution.

\subsubsection*{Droimate} in the first execution led to a sandbox that detected 64 apps with malicious behavior (66.66\%). Contrasting, in the original study Droidmate detected 54 among 102 (52.94\%). A possible explanation for this difference is that here we use the more recent version of Droidmate. In the second execution, without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect 48 out of the 96 pairs of Android apps.

\rb{I have read the paper until this point.}

\subsubsection*{Humanoid} at the first step of our study had the worse performance, identifying a little more than half of the pairs analyzed, 49 (51.04\%). It is the only tool not present at Bao et al work, so we could not compare our results with its work. Regarding the second part of the study, without static analysis, Humanoid was the most affected by this new situation, losing 69.38\% of its effectiveness, being able to detect just 15 pair apps malicious.

\subsubsection*{\joke}, as described, is a fake tool, that simulates a test tool that does not execute Android apps during a benchmark execution, considering just static analysis results. Even though Joke tool does not execute the Android apps, it was responsible to detect 43.75\% of malware, only aided by static analysis Droidfax, at the default configuration. Ignoring the influence of static analysis, since Joke tool depends exclusively on static analysis Droidfax, we suppose that it sandbox was unable to detect malware at our data set, result confirmed in our study, where Joke was unable to detect any malware, reducing its sandbox accuracy in 100\%.

Except for the \joke dummy tool, our studies show that 73.95\%-51.04\% of malicious pairs apps investigated, can be detected by the sandboxes constructed by others selected test generation tools, with de DroidXP default configuration. This first setup of our first study also shows that all the constructed sandboxes did not identify the malware in 19 pairs among 96 (19.79\%). These 19 malicious apps, according to Euphony tool \cite{hurier2017euphony}, that infer a single label per malicious application based on VirusTotal, were: 13 adwares, 3 trojans, 2 PUP (Potentially Unwanted Program) and 1 exploit. Table \ref{tab:malware} presents the number of malware detected by the sandboxes designed for each test case generation tool, with DroidXP default configuration, with static analysis Droidfax aid.

@@

\subsection{Result of the second study: Tainted analysis algorithms.}\label{sec:res-ss}

@@

\subsection{Discussion}\label{sec:discussion}
